Exploiting First-Class Arrays in Fortran for Accelerator Programming

### 2010-12-19 opencl/papers/performance.tex
Nearly at page limit.

Performance measurements were made comparing the transformed code with
different versions of the serial shallow-water code.  The serial
versions include the original written in C and two Fortran versions:
one using copy semantics for the regions and one using reference
semantics.  We also compare with a hand written OpenCL implementation
that was optimized for local memory usage (no array temporaries).  The
accelerated measurments were made using an NVIDIA Tesla C2050 (Fermi) cGPU with
2.625 GB GDDR5 memory, and 448 processor cores.  The serial
measurements were made using an Intel Xeon X5650 hexacore CPU with 96 GB of RAM
running at 2.67 GHz.  The compilers were gfortran and gcc version 4.4.3
with an optimization level of -O3.

@@

As can be seen in Figure~\ref{fig:cl-performance}, the transformed get very
good results of roughly 65 times speedup over the best Fortran code and YYY
speedup over the original C code.  It comes with XXX \% of the hand coded
OpenCL version.

>>>>

Performance measurements were made comparing the transformed code with
different versions of the serial shallow-water code.  The serial
versions include two separate Fortran versions:
one using data-parallel notation and the other using explicit looping
constructs.
We also compare with a hand-written OpenCL implementation
that was optimized for local memory usage (no array temporaries).  The
accelerated measurments were made using an NVIDIA Tesla C2050 (Fermi) cGPU with
2.625 GB GDDR5 memory, and 448 processor cores.  The serial
measurements were made using an Intel Xeon X5650 hexacore CPU with 96 GB of RAM
running at 2.67 GHz.  The compilers were gfortran and gcc version 4.4.3
with an optimization level of -O3.

@@

As can be seen in Figure~\ref{fig:cl-performance}, the transformed code achieves very
good results.  It is up to 40 times faster than the best serial Fortran code.
